---
title: "KNN on Oncogenic Cells"
author: "Adwesh Behera - 20025006"
date: "11 September 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
```

## Description

This is solution to "R - Programming: K-Nearest Neighbour Assignment" on Topcoder.

## Problem Statement

Routine breast cancer screening allows the disease to be diagnosed and treated prior to it causing noticeable symptoms. The process of early detection involves examining the breast tissue for abnormal lumps or masses. If a lump is found, a fine-needle aspiration biopsy is performed, which uses a hollow needle to extract a small sample of cells from the mass. A clinician then examines the cells under a microscope to determine whether the mass is likely to be malignant or benign.

If machine learning could automate the identification of cancerous cells, it would provide considerable benefit to the health system. Automated processes are likely to improve the efficiency of the detection process, allowing physicians to spend less time diagnosing and more time treating the disease. An automated screening system might also provide greater detection accuracy by removing the inherently subjective human component from the process.

Apply the k-NN algorithm to perform diagnosis Benign or Malignant

## The Dataset

The dataset for the above problem was imported from https://github.com/stedy/Machine-Learning-with-R-datasets/blob/master/wisc_bc_data.csv

s
```{r, echo=TRUE}
data = read.csv("wisc_bc_data.csv")
str(data)
data = data[-1]   #Removal of patient indices
```

## Including Libraries

The following libraries were needed to be installed and imported for the assignment.

```{r, echo=TRUE}
library(pca3d)
library(class)
library(gmodels)
library(ggbiplot)
```

## Principal Component Analysis

```{r, echo=TRUE}
#pca3d(princomp(data[,c(2:31)]), group = data$diagnosis)
ggbiplot(princomp(data[,c(2:31)]), groups = data$diagnosis, varname.size = 0)
```

The graph above shows the existance of spacial separation in the euclidian space between the two tumour catrgories.

## Pre-Processing : Normalization

```{r, echo=TRUE}
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x))) 
}

data_n = as.data.frame(lapply(data[2:31], normalize))
summary(data_n)
```

## Dividing Training and Test Data

We take N_sample rows as test cases and use the rest to train the classifier.

```{r, echo=TRUE}
N_sample = 100
s_index = sample(1:569, N_sample)
data_Train = data_n[-s_index,]
data_Test = data_n[s_index,]
```

## KNN

```{r, echo=TRUE}
N_K = 25
data_knn = knn(train = data_Train, test = data_Test, cl = data[-s_index, 1], k = N_K)
```

## Accuracy Analysis

The confusion matrix is shown below.

```{r, echo=TRUE}
CrossTable(x = data[s_index,1], data_knn)
```